Ms 1

### 2018-06-12 ms1/ms1_display.Rmd
small tweaks

```{r raw_drug_trends}
dummy = data_frame(
  year = rep(c(2011, 2014), 3),
  cpkp = c(0, 1500, 0, 250, 0, 100),
  panel = factor(c(1, 1, 2, 2, 3, 3)),
  abx = 'pde'
)

@@

cba_dat = claims_by_abx %>%
  bind_rows(approp_counts) %>%
  filter(antibiotic != 'n_pde_top10') %>%
  rename(abx=antibiotic) %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('n_pde', 'approp', 'inapp', 'indet') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  filter(!is.na(panel)) %>% # remove metro
  mutate(abx=case_when(
    .$abx == 'n_pde' ~ 'Overall use',
    .$abx == 'inapp' ~ 'Inappropriate use',
    .$abx == 'approp' ~ 'Appropriate use',
    .$abx == 'indet' ~ 'Indeterminate use',
    .$abx == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$abx == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp))

cba_dat %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text(
    data=filter(., year==2013),
    aes(label=abx),
    nudge_y=c(50, 50, -35, 35,
              26, -8, 10, 8, -8, -6,
              4, 8, -3, -5),
    nudge_x=c(0, rep(-0.5, 3),
              0, 0, 0, 0, 1.3, 0,
              rep(0, 4))
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank(),
        plot.margin=unit(c(1.0, 1.0, 0.5, 0.5), 'lines'),
        axis.text.x=element_text(color='black'),
        axis.text.y=element_text(color='black'),
        text=element_text(color='black')) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/raw_drug.pdf', height=5.0, width=9.0, unit='in')
ggsave('fig/drug_trends.png', height=5.0, width=9.0, unit='in')
```

@@

ggsave('fig/abx_trends.pdf', width=6.4, height=4.5, units='in')
ggsave('fig/abx_trends.png', width=6.4, height=4.5, units='in')
```

@@

```{r}
abx_trends %>%
  filter(antibiotic=='n_pde') %>%
  select(-antibiotic) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', estimate, lower_ci, upper_ci)) %>%
  mutate(p.value=format_p(p_value)) %>%
  kable
```

@@

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000)) %>%
  filter(year %in% c(2011, 2015)) %>%
  select(pop_char, value, year, cpkp) %>%
  spread(year, cpkp)

@@

```{r uti}
rxdx_kable(c('ciprofloxacin', 'trimethropim/sulfamethoxazole', 'nitrofurantoin'),
           c('uti', 'uti_t3'))
```

@@

```{r prescribing_practice_similarity}
rxdx_table_single = read_tsv('tables/pde_for_dx_single_counts.tsv') %>%
  left_join(denom, by='year') %>%
  mutate(cpkp = n_pdedx / n_bene * 1000)

rxdx_models_single = read_tsv('tables/pde_for_dx_single_models.tsv')

rxdx_comp = inner_join(rxdx_models, rxdx_models_single,
           by=c('antibiotic', 'dx_cat'),
           suffix=c('.multi', '.single'))

rxdx_comp %$%
  cor.test(estimate.multi, estimate.single)

lm(estimate.multi  ~ estimate.single, data=rxdx_comp) %>%
  summary()

rxdx_comp %>%
  ggplot(aes(estimate.multi, estimate.single,
             xmin=lower_ci.multi, xmax=upper_ci.multi,
             ymin=lower_ci.single, ymax=upper_ci.single)) +
  geom_abline() +
  geom_point() +
  geom_errorbar() + geom_errorbarh()
```

```{r prescribing_practice_single}
infection_sites = read_tsv('infection_sites.tsv')

combined_table_single = rxdx_table_single %>%
  mutate(cpkp=round(cpkp, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models_single, by=c('antibiotic', 'dx_cat')) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.1f ± %.1f', estimate, ceiling_at(pm, 1))) %>%
  mutate(p.value=format_p(p_value)) %>%
  left_join(infection_sites, by='dx_cat') %>%
  select(site, dx_cat, antibiotic, `2011`, `2014`, change, p.value) %>%
  arrange(site, dx_cat, antibiotic)

@@

>>>>

```{r raw_drug_trends}
dummy = data_frame(
  year = rep(c(2011, 2014), 3),
  cpkp = c(0, 1500, 0, 250, 0, 100),
  panel = factor(c(1, 1, 2, 2, 3, 3)),
  abx = 'n_pde'
)

@@

cba_dat = claims_by_abx %>%
  bind_rows(approp_counts) %>%
  filter(antibiotic != 'n_pde_top10') %>%
  rename(abx=antibiotic) %>%
  mutate(panel = factor(case_when(
    .$abx %in% c('n_pde', 'approp', 'inapp', 'indet') ~ 1,
    .$abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'trimethoprim/sulfamethoxazole', 'levofloxacin') ~ 2,
    .$abx %in% c('amoxicillin/clavulanate', 'doxycycline', 'nitrofurantoin', 'clindamycin') ~ 3
  ))) %>%
  filter(!is.na(panel)) %>% # remove metro
  mutate(abx=case_when(
    .$abx == 'n_pde' ~ 'Overall use',
    .$abx == 'inapp' ~ 'Potentially inappropriate use',
    .$abx == 'approp' ~ 'Potentially appropriate use',
    .$abx == 'indet' ~ 'Indeterminate use',
    .$abx == 'amoxicillin/clavulanate' ~ 'amox/clav',
    .$abx == 'trimethoprim/sulfamethoxazole' ~ 'TMP/SMX',
    TRUE ~ .$abx)
  ) %>%
  arrange(year, desc(cpkp))

cba_dat %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=dummy) +
  geom_line() +
  geom_text(
    data=filter(., year==2013),
    aes(label=abx),
    nudge_y=c(50, 55, -40, 40,
              26, -8, 10, 8, -8, -6,
              4, 8, -3, -5),
    nudge_x=c(0, -0.3, -0.3, -0.5,
              0, 0, 0, 0, 1.3, 0,
              rep(0, 4))
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank(),
        plot.margin=unit(c(1.0, 1.0, 0.5, 0.5), 'lines'),
        axis.text.x=element_text(color='black'),
        axis.text.y=element_text(color='black'),
        text=element_text(color='black')) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/raw_trends.pdf', height=5.0, width=9.0, unit='in')
ggsave('fig/raw_trends.png', height=5.0, width=9.0, unit='in')
```

@@

ggsave('fig/adjusted_trends.pdf', width=6.4, height=4.5, units='in')
ggsave('fig/adjusted_trends.png', width=6.4, height=4.5, units='in')
```

@@

```{r}
abx_trends %>%
  filter(antibiotic=='n_abx') %>%
  select(-antibiotic) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', estimate, lower_ci, upper_ci)) %>%
  mutate(p.value=format_p(p_value)) %>%
  kable(caption='Trends in overall use')
```

@@

## Retention

```{r}
retention_f = function(x) {
  n = length(x)
  c(1.0, x[2:n] / x[1:(n-1)])
}

retention_dat = read_tsv('tables/clean_bene_log.tsv')

retention_dat %>%
  filter(!(step %in% c('total', 'final'))) %>%
  group_by(year) %>%
  mutate(retention=retention_f(n_bene)) %>%
  ungroup() %>%
  mutate(step=factor(step, levels=c('20pct', 'over65', 'abd', 'demo')),
         n_bene=prettyNum(n_bene, big.mark=','),
         value=sprintf('%s (%.1f)', n_bene, 100*retention)) %>%
  select(year, step, value) %>%
  spread(year, value) %>%
  kable()
```

@@

```{r claims_by_demography}
subpop_table = read_tsv('tables/claims_by_subpop.tsv') %>%
  mutate(cpkp=round(n_pde/n_bene*1000, 2)) %>%
  filter(year %in% c(2011, 2015)) %>%
  select(pop_char, value, year, cpkp) %>%
  spread(year, cpkp)

@@

```{r uti}
rxdx_kable(c('ciprofloxacin', 'trimethoprim/sulfamethoxazole', 'nitrofurantoin'),
           c('uti', 'uti_t3'))
```

@@

```{r prescribing_practice_similarity}
infection_sites = read_tsv('db/infection_sites.tsv')

respiratory_dxs = infection_sites %>%
  filter(site=='resp') %>%
  pull(dx_cat)

rxdx_table_single = read_tsv('tables/pde_for_dx_single_counts.tsv') %>%
  filter(dx_cat %in% respiratory_dxs) %>%
  left_join(denom, by='year') %>%
  mutate(cpkp = n_pdedx / n_bene * 1000)

rxdx_models_single = read_tsv('tables/pde_for_dx_single_models.tsv') %>%
  filter(dx_cat %in% respiratory_dxs)
```

The two types of models give really similar results about trend estimates:

```{r}
inner_join(rxdx_models, rxdx_models_single,
           by=c('antibiotic', 'dx_cat'),
           suffix=c('.multi', '.single')) %>%
  mutate(f_diff=pmax(estimate.multi, estimate.single) / pmin(estimate.multi, estimate.single)) %$%
  max(f_diff)
```

But the number of claims should be different (line shows slope of 2):

```{r}
inner_join(rxdx_table, rxdx_table_single,
           by=c('antibiotic', 'dx_cat'),
           suffix=c('.multi', '.single')) %>%
  ggplot(aes(cpkp.single, cpkp.multi)) +
  geom_abline(slope=2) +
  geom_point()
```

```{r prescribing_practice_single}
combined_table_single = rxdx_table_single %>%
  mutate(cpkp=round(cpkp, 1)) %>%
  filter(year %in% c(2011, 2014)) %>%
  select(antibiotic, dx_cat, year, cpkp) %>%
  spread(year, cpkp) %>%
  right_join(rxdx_models_single, by=c('antibiotic', 'dx_cat')) %>%
  mutate_at(vars(estimate, lower_ci, upper_ci), est2pct) %>%
  mutate(pm=pmax(estimate-lower_ci, upper_ci-estimate)) %>%
  mutate(change=sprintf('%.1f ± %.1f', estimate, ceiling_at(pm, 1))) %>%
  mutate(p.value=format_p(p_value)) %>%
  select(dx_cat, antibiotic, `2011`, `2014`, change, p.value) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('azithromycin', 'levofloxacin', 'amoxicillin/clavulanate')),
         dx_cat=factor(dx_cat, levels=c('pneumonia', 'sinusitis', 'uri', 'bronchitis', 'other_resp', 'asthma'))) %>%
  arrange(dx_cat, antibiotic)

@@

# Reviewer response

## Print abstract figure

```{r print_abstract}
abstract_dummy = data_frame(
  year = rep(c(2011, 2015), 2),
  cpkp = c(0, 250, 0, 100),
  panel = factor(c(2, 2, 3, 3)),
  abx = 'pde'
)

abstract_panel_labels = c('2'='Top 6 most-used antibiotics',
                 '3'='Next 4 most-used antibiotics')

cba_dat %>%
  filter(panel %in% c(2, 3)) %>%
  {
  ggplot(., aes(x=year, y=cpkp, group=abx)) +
  geom_blank(data=abstract_dummy) +
  geom_line() +
  geom_text(
    data=filter(., year==2013),
    aes(label=abx),
    nudge_y=c(26, -8, 10, 8, -8, -6,
              4, 8, -3, -5),
    nudge_x=c(0, 0, 0, 0, 1.3, 0,
              rep(0, 4))
  ) +
  facet_wrap(~panel, scales='free_y', labeller=labeller(panel=abstract_panel_labels)) +
  theme_classic() +
  theme(panel.grid.minor.x=element_blank(),
        strip.background = element_blank(),
        plot.margin=unit(c(1.0, 1.0, 0.5, 0.5), 'lines'),
        axis.text.x=element_text(color='black'),
        axis.text.y=element_text(color='black'),
        text=element_text(color='black')) +
  scale_x_continuous(expand=c(0, 0), name='') +
  scale_y_continuous(expand=c(0, 0), name='claims per 1,000 beneficiaries per year')
  }

ggsave('fig/abstract_fig.pdf', height=5.0, width=6.0, unit='in')
ggsave('fig/abstract_fig.png', height=5.0, width=6.0, unit='in')
```

## Stacked bar charts

```{r stacked_trends}
p = cba_dat %>%
  filter(panel != 1) %>%
  mutate(abx=fct_reorder(factor(abx), cpkp)) %>%
  ggplot(aes(x=year, y=cpkp, fill=abx)) +
  geom_col(color='black') +
  xlab('') +
  ylab('Claims per 1,000 beneficiaries per year') +
  theme_minimal() +
  theme(legend.title=element_blank())

show(p)
ggsave(plot=p, 'fig/stacked_trends.pdf', units='in', width=4, height=3)
```
